---
title: "Using CI"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Load library
```{r ci1}
library(CI)
library(MASS)
```

Generate data for analysis
```{r ci2}
cr = 0.95
df <- mvrnorm(50, mu = c(0,0), Sigma = matrix(c(1,cr,cr,1), ncol = 2), empirical = TRUE)
```

Calculate concordance index
```{r ci3}
CI(x=df[,1], y=df[,2], deltaX=0, deltaY=0, alpha =0, outx = 1, npermut=10000)
```




Calculate correlations
```{r ci4}
cor.test(df[,1], df[,2])
cor.test(df[,1], df[,2], method = "pearson")
cor.test(df[,1], df[,2], method = "spearman")
```



## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:100)
plot(100:1)
```
You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
